\mytitle

### 2023-05-06 chapters/intro.tex
1.3 (depsyth in intro)

\chapter{Introduction}

@@

\section{Automatic Crash Consistency with Synthesis}
% TODO
% DepSynth: consider storage mechanism separately from crash consistency mechanism (TODO)
% DepSynth: design rules language to describe any runtime dependencies (TODO)

\section{Contributions}
The remainder of this dissertation is broken into two chapters.
The first presents \jitsynth, a tool for synthesizing just-in-time compilers for
in-kernel DSLs.
k

>>>>

\chapter{Introduction}
% Both of the works presented in this dissertation take advantage of two key ideas
% in order to effectively specialize for their respective domains.
% ...
% The first of these ideas is to simplify the synthesis task with system decomposition...
% The second key idea is leveraging system-specific metaprogramming abstractions...

@@

\section{Automatic Crash Consistency with Synthesis}
Storage systems face an increasing demand for reliability.
From Linux file systems to Amazon cloud-based key-value stores,
storage systems must maintain the integrity of their data
even in the presence of system crashes.
This property of storage systems is known as \textit{crash consistency}.
Guaranteeing crash consistency is a highly non-trivial task for developers,
as it requires maintaining complex invariants that depend greatly on
storage system implementation details.
Moreover, failing to guarantee crash consistency may result in severe impacts,
including costly slowdowns and massive data losses. % TODO make more concrete
% TODO finish: Highlight what can go wrong if crash consistency is done incorrectly
% TODO
% DepSynth: consider storage mechanism separately from crash consistency mechanism (TODO)
% DepSynth: design rules language to describe any runtime dependencies (TODO)

\cref{c:depsynth} presents \depsynth, a tool for automatically generating crash consistency
code for storage systems.
\depsynth takes advantage of the observation
(identified in previous work \todo{cite Featherstitch})
that crash consistency mechanisms fundamentally enforce \textit{write-before relationships}.
To automate crash consistency,
\depsynth takes as input the implementation of a (non-crash consistent) storage system together
with a set of example programs over the system called \textit{litmus tests}.
The output is a set of \textit{dependency rules} which specify, at runtime,
the required write-before relationships to enforce.

% TODO revise this paragraph
We take advantage of several novel abstractions in order enable
automatic crash consistency with \depsynth.
First, we assume a new \textit{angelic crash consistency} model
that delegates enforcement of write-before relationships to a
\textit{dependency-aware buffer cache}
that sits between the storage system software and hardware layers.
Second, we introduce a language for dependency rules
that allows for both \textit{expressive} and \textit{generalizable} rules.
Finally, we describe a new search for dependency rules
directed by input litmus tests.
These insights enable \depsynth to synthesize dependency rules for an existing
production key-value store at Amazon\todo{cite shardstore} in 49\todo{macro this} minutes.

\section{Contributions}
The remainder of this dissertation is broken into two chapters.
% TODO
%\cref{c:jitsynth} presents \jitsynth and the techniques that enable
%\jitsynth to synthesize in-kernel JIT compilers.
%\cref{c:depsynth} presents \depsynth and the techniques that enable
